Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-12-16 paper/main.tex
more rearranging/strippng out O_A

$\vartist: \sheaf^{\vindex^*} \rightarrow \sheaf_{\vartist}$, it follows from \autoref{eq:related-work:equivariance:functor_diagram} that an arbitrary morphism $\dfunc$ on the data sheaf has a compatible morphism $\dfunc^{\prime}$ on the graphic sheaf. 
\begin{equation}
  \label{eq:artist:morphism_of_functors}
  \begin{tikzcd}
    \sheafc_{\vindexc^{*}} \arrow[d, "\dfuncc"', color=action] \arrow[r, "\vartistc", color=artist] & \sheafc_{\vartistc} \arrow[d, "\dfuncpc \coloneqq\vartistc(\dfuncc)", color=action] \\
    \sheafc_{\vindexc^{*}} \arrow[r, "\vartistc"', color=artist]                      & \sheafc_{\vartistc}     
    \end{tikzcd}
\end{equation}
As a consequence of \autoref{eq:artist:morphism_of_functors},

@@

\note{valid $\rho$ is determined by equivariance, which we haven't introduced yet, but we can introduce equivariance w/ just $\sheaf_{\gtotal}$}
\begin{equation}
  \label{eq:artist:artist_sheaf}
  \begin{tikzcd}[column sep=tiny, row sep=huge]
    {\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}}&  & 
    \textcolor{set}{\big\{}\gsectionc:\opensetgc\rightarrow \gtotalc\restriction_{\opensetgc} 
    \bigm{\vert} \vartistc\circ\dfuncc \circ \vartistc^{-1}[\gsectionc] = \dfuncc^{\prime} \circ \gsectionc, \dsectionc \in \sheafc_{\dtotal}
    \textcolor{set}{\big\}} 
    \arrow[ll, "\textcolor{set}{\mathlarger{\mathlarger{\supset}}}" description, hook', color=white] \\ &  & \\
    \opensetgc \arrow[uu, "\sheafc_{\gtotalc}", color=sheaf] \arrow[rruu, "\vartistc(\sheafc_{\dtotalc})\coloneqq \sheafc_{\vartistc}" description, dashed, color=sheaf] &  & 
    \end{tikzcd}
\end{equation}

>>>>

It follows from \autoref{eq:related-work:equivariance:functor_diagram} that an arbitrary morphism $\dfunc$ on the data sheaf has a compatible morphism $\dfunc^{\prime}$ on the graphic sheaf. 
\begin{equation}
  \label{eq:artist:morphism_of_functors}
  \begin{tikzcd}
    \sheafc_{\dtotalc} \arrow[d, "\dfuncc"', color=action] \arrow[r, "\vartistc_{\vindexpullc}", color=artist] & \sheafc_{\gtotalc} \arrow[d, "\dfuncpc \coloneqq\vartistc_{\vindexpullc}(\dfuncc)", color=action] \\
    \sheafc_{\dtotalc} \arrow[r, "\vartistc_{\vindexpullc}"', color=artist]                      & \sheafc_{\gtotalc}     
    \end{tikzcd}
\end{equation}
As a consequence of \autoref{eq:artist:morphism_of_functors},

@@

\note{valid $\rho$ is determined by equivariance, which we haven't introduced yet, but we can introduce equivariance w/ just $\sheaf_{\gtotal}$}
\begin{equation}
  \label{eq:artist:artist_sheaf}
  \begin{tikzcd}[column sep=tiny, row sep=huge]
    {\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}}&  & 
    \textcolor{set}{\big\{}\gsectionc:\opensetgc\rightarrow \gtotalc\restriction_{\opensetgc} 
    \bigm{\vert} \vartistc\circ (\dfuncc \circ \vartistc^{-1}[\gsectionc]) = \dfuncc^{\prime} \circ \gsectionc \textcolor{set}{\big\}} 
    \arrow[ll, "\textcolor{set}{\mathlarger{\mathlarger{\supset}}}" description, hook', color=white] \\ &  & \\
    \opensetgc \arrow[uu, "\sheafc_{\gtotalc}", color=sheaf] \arrow[rruu, "\vartistc(\sheafc_{\dtotalc})\coloneqq \sheafc_{\vartistc}" description, dashed, color=sheaf] &  & 
    \end{tikzcd}
\end{equation}
